Price of Anarchy for Mean Field Games

### 2018-07-04 PoA.tex
Major point 2 fixed

To begin, we need to describe in more detail the two problems that will be used to compute the price of anarchy: the linear quadratic extended mean field game, and the linear quadratic control problem of McKean-Vlasov type with dependence on the law of the control. To specify the problems, we only need to specify the drift and cost functions, $b$, $f$, and $g$ introduced in Section \ref{se:introduction}. For the linear quadratic models, we take the drift to be linear:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=b_1(t)x+\bar{b}_1(t) \bar{\mu}+b_2(t) \alpha+\bar{b}_2(t) \bar{\nu},
\end{equation*}
where $\bar{\mu}$ denotes the mean of the measure $\mu$, namely, $\bar{\mu}=\int_{\mathbb{R}}xd\mu(x)$, and similarly for $\bar{\nu}$. We take the running and terminal costs to be quadratic:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right), \\
    g(x,\mu)&=\frac{1}{2}\left(q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right).
\end{split}
\end{equation*}
\begin{remark}
If $\bar{b}_2(t)\equiv0$ and $\bar{r}(t)\equiv0$, then we have the standard mean field game or control problem of McKean-Vlasov type. (See Theorem \ref{th:exist_uniq} for assumptions that provide existence and uniqueness.)
\end{remark}

\subsection{\textbf{Linear Quadratic Extended Mean Field Games}}\label{sec:EMFG}
To solve the linear quadratic extended mean field game (LQEMFG), we begin by considering the reduced Hamiltonian for this problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y \\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right),
\end{split}
\end{equation*}
and whenever the flows $\bmubar=(\bar{\mu}_t)_{0\leq t\leq T}$ and $\bnubar=(\bar{\nu}_t)_{0\leq t\leq T}$ are fixed, we consider for each control process $\balpha=(\alpha_t)_{0\leq t\leq T}$ the adjoint equation:

@@

This is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem. Then from the appendix, we have:
\begin{equation*}
\begin{split}
\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-\bar{q}s_T))&=0,
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
\end{equation*}
\begin{equation*}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
\end{equation*}
Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
\end{equation*}
Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
\begin{equation*}
\begin{split}
    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
    &+(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
\end{equation*}

\subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
To solve the linear quadratic optimal control problem of McKean-Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right).
\end{split}
\end{equation*}
Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality. A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}. This sufficient condition is the following:
$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
\begin{equation*}
    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t)(X_t,\hat{\alpha}_t) \right]=0,
\end{equation*}
where the adjoint equation is given by:
\begin{equation*}
\begin{split}
    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\mu}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t)(X_t,\alpha_t) \right] \right]dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
\end{split}
\end{equation*}
where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.

In the present LQ case, the sufficient condition can be used to solve for:
\begin{equation*}
    \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
and:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
\end{split}
\end{equation*}
So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMKV}
\end{equation}
with initial condition $X_0=\xi$, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T+s_T\bar{q}_T(s_T-2)\mathbb{E}X_T$.

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation*}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation*}
\begin{equation*}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\end{equation*}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

>>>>

To begin, we need to describe in more detail the two problems that will be used to compute the price of anarchy: the linear quadratic extended mean field game, and the linear quadratic control problem of McKean-Vlasov type with dependence on the law of the control. To specify the problems, we only need to specify the drift and cost functions, $b$, $f$, and $g$ introduced in Section \ref{se:introduction}. For the linear quadratic models, we take the drift to be linear:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=b_1(t)x+\bar{b}_1(t) \bar{\mu}+b_2(t) \alpha+\bar{b}_2(t) \bar{\nu},
\end{equation*}
where $\bar{\mu}$ denotes the mean of the measure $\mu$, namely, $\bar{\mu}=\int_{\mathbb{R}}xd\mu(x)$, and similarly for $\bar{\nu}$. We take the running and terminal costs to be quadratic:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right), \\
    g(x,\mu)&=\frac{1}{2}\left(q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right).
\end{split}
\end{equation*}
\begin{remark}
If $\bar{b}_2(t)\equiv0$ and $\bar{r}(t)\equiv0$, then we have the standard mean field game or control problem of McKean-Vlasov type. (See Theorem \ref{th:exist_uniq} for assumptions that provide existence and uniqueness.)
\end{remark}

\subsection{\textbf{Linear Quadratic Extended Mean Field Games}}\label{sec:EMFG}
To solve the linear quadratic extended mean field game (LQEMFG), we begin by considering the reduced Hamiltonian for this problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y \\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right),
\end{split}
\end{equation*}
and whenever the flows $\bmubar=(\bar{\mu}_t)_{0\leq t\leq T}$ and $\bnubar=(\bar{\nu}_t)_{0\leq t\leq T}$ are fixed, we consider for each control process $\balpha=(\alpha_t)_{0\leq t\leq T}$ the adjoint equation:

@@

This is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem. Then from the appendix, we have:
\begin{equation*}
\begin{split}
\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-\bar{q}s_T))&=0,
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
\end{equation*}
\begin{equation*}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
\end{equation*}
Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
\end{equation*}
Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
\begin{equation*}
\begin{split}
    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
    &+(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
\end{equation*}

\subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
To solve the linear quadratic optimal control problem of McKean-Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right).
\end{split}
\end{equation*}
Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality. A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}. Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
\begin{equation*}
    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t) \right]=0,
\end{equation*}
where the adjoint equation is given by:
\begin{equation*}
\begin{split}
    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
\end{split}
\end{equation*}
and $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$. In the present LQ case, the sufficient condition can be used to solve for:
\begin{equation*}
    \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
and:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
\end{split}
\end{equation*}
So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMKV}
\end{equation}
with initial condition $X_0=\xi$, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T+s_T\bar{q}_T(s_T-2)\mathbb{E}X_T$.

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation*}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation*}
\begin{equation*}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation*}
\begin{equation*}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\end{equation*}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}
